Fast, Scalable Phrase-Based SMT Decoding

### 2016-02-08 acl.2016/acl2016.tex
acl paper

\section{BLAH BLAH}

The following instructions are directed to authors of papers submitted to and accepted
for publication in the ACL 2016 proceedings.  All authors are required
to adhere to these specifications. Authors are required to provide 
a Portable Document Format (PDF) version of
their papers.  The proceedings will be printed on A4 paper.
Authors from countries where access to word-processing systems is
limited should contact the publication chairs as soon as possible.
 Grayscale readability of all figures and
graphics will be encouraged for all accepted papers
(Section \ref{ssec:accessibility}).

Submitted and camera-ready formatting is similar,
  however, the submitted paper should have:
\begin{enumerate} 
\item Author-identifying information removed
\item A `ruler' on the left and right margins
\item Page numbers 
\item A confidentiality header.  
\end{enumerate}
In contrast, the camera-ready {\bf should  not have} a ruler, page numbers, nor a confidentiality header.  By uncommenting {\small\verb|\aclfinalcopy|} at the top of this 
 document, it will compile to produce an example of the camera-ready formatting; by leaving it commented out, the document will be anonymized for initial submission.  Authors should place this command after the {\small\verb|\usepackage|} declarations when preparing their camera-ready manuscript with the ACL 2016 style.

\section{General Instructions}

Manuscripts must be in two-column format.  Exceptions to the
two-column format include the title, as well as the 
authors' names and complete
addresses (only in the final version, not in the version submitted for review), 
which must be centered at the top of the first page (see
the guidelines in Subsection~\ref{ssec:first}), and any full-width
figures or tables.  Type single-spaced.  Do not number the pages 
in the camera-ready version.
Start all pages directly under the top margin.  See the guidelines
later regarding formatting the first page.

The maximum length of a manuscript is eight (8) pages for the main
conference, printed single-sided, plus two (2) pages for references
(see Section~\ref{sec:length} for additional information on the
maximum number of pages).

By uncommenting {\small\verb|\aclfinalcopy|} at the top of this 
 document, it will compile to produce an example of the camera-ready formatting; by leaving it commented out, the document will be anonymized for initial submission.  When you first create your submission on softconf, please fill in your submitted paper ID where {\small\verb|***|} appears in the {\small\verb|\def\aclpaperid{***}|} definition at the top.

The review process is double-blind, so do not include any author information (names, addresses) when submitting a paper for review.  
However, you should maintain space for names and addresses so that they will fit in the final (accepted) version.  The ACL 2016 \LaTeX\ style will create a titlebox space of 2.5in for you when {\small\verb|\aclfinalcopy|} is commented out.

\subsection{The Ruler}
The ACL 2016 style defines a printed ruler which should be presented in the
version submitted for review.  The ruler is provided in order that
reviewers may comment on particular lines in the paper without
circumlocution.  If you are preparing a document without the provided
style files, please arrange for an equivalent ruler to
appear on the final output pages.  The presence or absence of the ruler
should not change the appearance of any other content on the page.  The
camera ready copy should not contain a ruler. (\LaTeX\ users may uncomment
the {\small\verb|\aclfinalcopy|} command in the document preamble.)

Reviewers:
note that the ruler measurements do not align well with lines in the paper
--- this turns out to be very difficult to do well when the paper contains
many figures and equations, and, when done, looks ugly.  Just use fractional
references (e.g., the first line on this page is at mark $096.5$), although in most cases one would
expect that the approximate location will be adequate.

\subsection{Electronically-available resources}

ACL provides this description in \LaTeX2e{} ({\small\tt acl2016.tex}) and PDF
format ({\small\tt acl2016.pdf}), along with the \LaTeX2e{} style file used to
format it ({\small\tt acl2016.sty}) and an ACL bibliography style ({\small\tt acl2016.bst})
and example bibliography ({\small\tt acl2016.bib}).
These files are all available at
{\small\tt acl2016.org/index.php?article\_id=9}. We
strongly recommend the use of these style files, which have been
appropriately tailored for the ACL 2016 proceedings.

\subsection{Format of Electronic Manuscript}
\label{sect:pdf}

For the production of the electronic manuscript, you must use Adobe's
Portable Document Format (PDF). This format can be generated from
postscript files: on Unix systems, you can use {\small\tt ps2pdf} for this
purpose; under Microsoft Windows, you can use Adobe's Distiller, or
if you have cygwin installed, you can use {\small\tt dvipdf} or
{\small\tt ps2pdf}.  Note 
that some word processing programs generate PDF that may not include
all the necessary fonts (esp.\ tree diagrams, symbols). When you print
or create the PDF file, there is usually an option in your printer
setup to include none, all, or just non-standard fonts.  Please make
sure that you select the option of including ALL the fonts.  {\em
  Before sending it, test your {\/\em PDF} by printing it from a
  computer different from the one where it was created}. Moreover,
some word processors may generate very large postscript/PDF files,
where each page is rendered as an image. Such images may reproduce
poorly.  In this case, try alternative ways to obtain the postscript
and/or PDF.  One way on some systems is to install a driver for a
postscript printer, send your document to the printer specifying
``Output to a file'', then convert the file to PDF.

For reasons of uniformity, Adobe's {\bf Times Roman} font should be
used. In \LaTeX2e{} this is accomplished by putting
\small
\begin{verbatim}
\usepackage{times}
\usepackage{latexsym}
\end{verbatim}
\normalsize
in the preamble.

Print-outs of the PDF file on A4 paper should be identical to the
hardcopy version.  If you cannot meet the above requirements about the
production of your electronic submission, please contact the
publication chairs above  as soon as possible.

\subsection{The First Page}
\label{ssec:first}

Center the title, author name(s) and affiliation(s) across both
columns (or, in the case of initial submission, space for the names). 
Do not use footnotes for affiliations.  
Use the two-column format only when you begin the abstract.

{\bf Title}: Place the title centered at the top of the first page, in
a 15 point bold font.  (For a complete guide to font sizes and styles, see Table~\ref{font-table}.)
Long titles should be typed on two lines without
a blank line intervening. Approximately, put the title at 1in from the
top of the page, followed by a blank line, then the author name(s),
and the affiliation(s) on the following line.  Do not use only initials
for given names (middle initials are allowed). Do not format surnames
in all capitals (e.g., ``Mitchell,'' not ``MITCHELL'').  The affiliation should
contain the author's complete address, and if possible, an electronic
mail address. Leave about 0.75in between the affiliation and the body
of the first page.

{\bf Abstract}: Type the abstract at the beginning of the first
column.  The width of the abstract text should be smaller than the
width of the columns for the text in the body of the paper by about
0.25in on each side.  Center the word {\bf Abstract} in a 12 point
bold font above the body of the abstract. The abstract should be a
concise summary of the general thesis and conclusions of the paper.
It should be no longer than 200 words.  The abstract text should be in 10 point font.

\begin{table}
\centering
\small
\begin{tabular}{cc}
\begin{tabular}{|l|l|}
\hline
{\bf Command} & {\bf Output}\\\hline
\verb|{\"a}| & {\"a} \\
\verb|{\^e}| & {\^e} \\
\verb|{\`i}| & {\`i} \\ 
\verb|{\.I}| & {\.I} \\ 
\verb|{\o}| & {\o} \\
\verb|{\'u}| & {\'u}  \\ 
\verb|{\aa}| & {\aa}  \\\hline
\end{tabular} & 
\begin{tabular}{|l|l|}
\hline
{\bf Command} & {\bf  Output}\\\hline
\verb|{\c c}| & {\c c} \\ 
\verb|{\u g}| & {\u g} \\ 
\verb|{\l}| & {\l} \\ 
\verb|{\~n}| & {\~n} \\ 
\verb|{\H o}| & {\H o} \\ 
\verb|{\v r}| & {\v r} \\ 
\verb|{\ss}| & {\ss} \\\hline
\end{tabular}
\end{tabular}
\caption{Example commands for accented characters, to be used in, e.g., \BibTeX\ names.}\label{tab:accents}
\end{table}

{\bf Text}: Begin typing the main body of the text immediately after
the abstract, observing the two-column format as shown in 
the present document.  Do not include page numbers in the camera-ready manuscript.

{\bf Indent} when starting a new paragraph. For reasons of uniformity,
use Adobe's {\bf Times Roman} fonts, with 11 points for text and 
subsection headings, 12 points for section headings and 15 points for
the title.  If Times Roman is unavailable, use {\bf Computer Modern
  Roman} (\LaTeX2e{}'s default; see section \ref{sect:pdf} above).
Note that the latter is about 10\% less dense than Adobe's Times Roman
font.

\subsection{Sections}

{\bf Headings}: Type and label section and subsection headings in the
style shown on the present document.  Use numbered sections (Arabic
numerals) in order to facilitate cross references. Number subsections
with the section number and the subsection number separated by a dot,
in Arabic numerals.

{\bf Citations}: Citations within the text appear
in parentheses as~\cite{Gusfield:97} or, if the author's name appears in
the text itself, as Gusfield~\shortcite{Gusfield:97}.  Using the provided \LaTeX\ style, the former is accomplished using
{\small\verb|\cite|} and the latter with {\small\verb|\shortcite|} or {\small\verb|\newcite|}.  Collapse multiple citations as in~\cite{Gusfield:97,Aho:72}; this is accomplished with the provided style using commas within the {\small\verb|\cite|} command, e.g., {\small\verb|\cite{Gusfield:97,Aho:72}|}.  
Append lowercase letters to the year in cases of ambiguities.  
Treat double authors as in~\cite{Aho:72}, but write as 
in~\cite{Chandra:81} when more than two authors are involved.

\textbf{References}:  We recommend
including references in a separate~{\small\texttt .bib} file, and include an example file 
in this release ({\small\tt naalhlt2016.bib}).  Some commands
for names with accents are provided for convenience in Table \ref{tab:accents}.  
References stored in the separate~{\small\tt .bib} file are inserted into the document using the following commands:

\small
\begin{verbatim}
\bibliography{acl2016}
\bibliographystyle{acl2016}
\end{verbatim}
\normalsize

References should appear under the heading {\bf References} at the 
end of the document, but before any Appendices, unless the appendices contain references.  
Arrange the references alphabetically
by first author, rather than by order of occurrence in the text.  %This behavior is provided by default in the provided \BibTeX\ style ({\small\tt naaclhlt2016.bst}). 
Provide as complete a reference as possible, using a consistent format,
such as the one for {\em Computational Linguistics\/} or the one in the 
{\em Publication Manual of the American 
Psychological Association\/}~\cite{APA:83}.  Authors' full names rather than initials are preferred.  You may use
{\bf standard} abbreviations for conferences\footnote{\scriptsize {\tt https://en.wikipedia.org/wiki/ \\ \-\hspace{.75cm} List\_of\_computer\_science\_conference\_acronyms}} and journals\footnote{\tt http://www.abbreviations.com/jas.php}.

{\bf Appendices}: Appendices, if any, directly follow the text and the
references (but see above).  Letter them in sequence and provide an
informative title: {\bf Appendix A. Title of Appendix}.

\textbf{Acknowledgment} sections should go as a last (unnumbered) section immediately
before the references.

\subsection{Footnotes}

{\bf Footnotes}: Put footnotes at the bottom of the page. They may
be numbered or referred to by asterisks or other
symbols.\footnote{This is how a footnote should appear.} Footnotes
should be separated from the text by a line.\footnote{Note the
line separating the footnotes from the text.}  Footnotes should be in 9 point font.

\subsection{Graphics}

{\bf Illustrations}: Place figures, tables, and photographs in the
paper near where they are first discussed, rather than at the end, if
possible.  Wide illustrations may run across both columns and should be placed at
the top of a page. Color illustrations are discouraged, unless you have verified that 
they will be understandable when printed in black ink.

\begin{table}
\small
\centering
\begin{tabular}{|l|rl|}
\hline \bf Type of Text & \bf Font Size & \bf Style \\ \hline
paper title & 15 pt & bold \\
author names & 12 pt & bold \\
author affiliation & 12 pt & \\
the word ``Abstract'' & 12 pt & bold \\
section titles & 12 pt & bold \\
document text & 11 pt  &\\
abstract text & 10 pt & \\
captions & 9 pt & \\
caption label & 9 pt & bold \\
bibliography & 10 pt & \\
footnotes & 9 pt & \\
\hline
\end{tabular}
\caption{\label{font-table} Font guide.}
\end{table}

{\bf Captions}: Provide a caption for every illustration; number each one
sequentially in the form:  ``{\bf Figure 1:} Figure caption.'', ``{\bf Table 1:} Table caption.''  Type the captions of the figures and 
tables below the body, using 9 point text.  Table and Figure labels should be bold-faced.

\subsection{Accessibility}
\label{ssec:accessibility}

In an effort to accommodate the color-blind (as well as those printing
to paper), grayscale readability for all accepted papers will be
encouraged.  Color is not forbidden, but authors should ensure that
tables and figures do not rely solely on color to convey critical
distinctions.
Here we give a simple criterion on your colored figures, if your paper has to be printed in black and white, then you must assure that every curves or points in your figures can be still clearly distinguished.

\section{Length of Submission}
\label{sec:length}

The ACL 2016 main conference accepts submissions of long papers and short papers.  Long papers may consist of up to eight (8) pages of content, plus unlimited pages for references. Upon acceptance, final versions of long papers will be given one additional page (up to 9 pages with unlimited pages for references) so that reviewers' comments can be taken into account.  Short papers may consist of up to four (4) pages of content, plus unlimited pages for references. Upon acceptance, short papers will be given five (5) pages in the proceedings and unlimited pages for references.  For both long and short papers, all illustrations and appendices must be accommodated within these page limits, observing the formatting instructions given in the present document.  Papers that do not conform to the specified length and formatting requirements are subject to be rejected without review.

\section{Double-blind review process}
\label{sec:blind}

As the reviewing will be blind, the paper must not include the
authors' names and affiliations.  Furthermore, self-references that
reveal the author's identity, e.g., ``We previously showed (Smith,
1991) ...'' must be avoided. Instead, use citations such as ``Smith
previously showed (Smith, 1991) ...'' Papers that do not conform to
these requirements will be rejected without review. In addition,
please do not post your submissions on the web until after the
review process is complete (in special cases this is permitted: see 
the multiple submission policy below).

We will reject without review any papers that do not follow the
official style guidelines, anonymity conditions and page limits.

\section{Multiple Submission Policy}

Papers that have been or will be submitted to other meetings or
publications must indicate this at submission time. Authors of
papers accepted for presentation at ACL 2016 must notify the
program chairs by the camera-ready deadline as to whether the paper
will be presented. All accepted papers must be presented at the
conference to appear in the proceedings. We will not accept for
publication or presentation papers that overlap significantly in
content or results with papers that will be (or have been) published
elsewhere.

Preprint servers such as arXiv.org and ACL-related workshops that
do not have published proceedings in the ACL Anthology are not
considered archival for purposes of submission. Authors must state
in the online submission form the name of the workshop or preprint
server and title of the non-archival version.  The submitted version
should be suitably anonymized and not contain references to the
prior non-archival version. Reviewers will be told: ``The author(s)
have notified us that there exists a non-archival previous version
of this paper with significantly overlapping text. We have approved
submission under these circumstances, but to preserve the spirit
of blind review, the current submission does not reference the
non-archival version.'' Reviewers are free to do what they like with
this information.

Authors submitting more than one paper to ACL must ensure
that submissions do not overlap significantly ($>25\%$) with each other
in content or results. Authors should not submit short and long
versions of papers with substantial overlap in their original
contributions.

\section*{Acknowledgments}

Do not number the acknowledgment section.
This section should not be presented for the submission version.

>>>>

% \section*{Acknowledgments}
% 
% Do not number the acknowledgment section.
% This section should not be presented for the submission version.
